#FCBF networks

Our goal here is to explore the FCBF package as a tool for building co-expression networks.


```{r Packages required}
devtools::install_github('lubianat/FCBF')
library(FCBF)
library(Seurat)
library(dplyr)
library(igraph)

```

```{r Example data}
# the Seurat object that is produced in Seurat's v2.0 tutorial
pbmc <- readRDS("./data/pbmc_tutorial.rds")
exprs <- as.data.frame(as.matrix(pbmc@data))
target <- as.factor(pbmc@ident)
rm(list=("pbmc"))
```


Let's start by discretizing the data using FCBF's supervised discretize exprs.

```{r Discretizing the data}
set.seed(3)
discretized_exprs <- FCBF::discretize_exprs_supervised(exprs, target)

```

Now that we have a discretized gene expression table, we can proceed to start making the network. 

```{r}
# get the SU scores
symetrical_uncertainty_scores <- FCBF::get_su(discretized_exprs, target)
symetrical_uncertainty_scores$gene <- rownames(symetrical_uncertainty_scores)

colnames(symetrical_uncertainty_scores)[1] <- 'SU'

fcbf_filtered <- fcbf(discretized_exprs, target, thresh = 0.2, verbose = T)
fcbf_filtered$gene <- rownames(fcbf)

FCBF_genes <- gsub('\\.', '-', fcbf_filtered$gene)

```

There are two relevant table at the moment : the SU scored for all genes, and the genes selected by FCBF. 

Step 1:
    - Set an SU threshold to filter the total table
    
In this way, the genes that make up the final network will be related to the class of interest.



```{r}
SU_threshold <- 0.2 

symetrical_uncertainty_scores_small <- symetrical_uncertainty_scores[symetrical_uncertainty_scores$SU > SU_threshold,]


SU_genes <- gsub('\\.', '-',symetrical_uncertainty_scores_small[,2])


exprs_small <- discretized_exprs[SU_genes ,]
```


Now we have what is needed to calculate the correlations for the network. 



```{r}
edgelist <- data.frame(1,1,1)
edgelist <- edgelist[-1,]


for (i in bla) {
print(i)
gene_i <- as.factor(discretized_exprs[i, ])
gene_i_correlates <-
get_su(x = mini_exprs, y = as.factor(mini_exprs[i, ]))
gene_i_correlates$gene <- rownames(gene_i_correlates)
gene_i_correlates$su_ic <-
su_supdis$`sort(su_ic, decreasing = T)`[match(gene_i_correlates$gene, su_supdis$gene)]
gene_i_correlates$fcbf_removed <-
ifelse(
gene_i_correlates$su_ic <  gene_i_correlates$`sort(su_ic, decreasing = T)`,
'removed',
'kept'
)
gene_i_correlates <-
gene_i_correlates[complete.cases(gene_i_correlates), ]

gene_i_correlates <-
gene_i_correlates[gene_i_correlates$fcbf_removed == "removed", ]
edges_for_gene_i <-
data.frame(
EdgeA = sample(i, length(gene_i_correlates$gene), replace = T),
EdgeB = gsub('\\.', '-', gene_i_correlates$gene),
Weight = gene_i_correlates$`sort(su_ic, decreasing = T)`
)
edgelist <- rbind(edgelist, edges_for_gene_i)
}

edgelist_final <-
edgelist[as.character(edgelist$EdgeA) != as.character(edgelist$EdgeB),]

edgelist_final <-
edgelist_final[!(paste(edgelist$EdgeA, edgelist$EdgeB) %in% paste(edgelist$EdgeB, edgelist$EdgeA)),]
library(igraph)
edgelist_final <-  droplevels(edgelist_final)
edgelist_final <- edgelist_final[complete.cases(edgelist_final),]
adj <- tidyr::spread(edgelist_final, key = EdgeB, value = Weight)
adj[is.na(adj)] <- 0
rownames(adj) <- adj$EdgeA
adj$EdgeA <- NULL
bla <- read.graph()
g <- graph_from_incidence_matrix(adj, weighted = T, directed = F)
hs <- hub_score(g, weights = NA)$vector
plot(
g,
vertex.size = 4,
vertex.label.dist = 0,
edge.curved = .2,
vertex.label.font = 1,
vertex.label.cex = .5
)
```

