#FCBF networks

Our goal here is to explore the FCBF package as a tool for building co-expression networks.


```{r Packages required}
devtools::install_github('lubianat/FCBF')
library(FCBF)
library(Seurat)
library(dplyr)
library(igraph)

```

```{r Example data}
data("pbmc_small")
exprs <- as.data.frame(as.matrix(pbmc_small@data))
target <- as.factor(pbmc_small@ident)
```


Let's start by discretizing the data using FCBF's supervised discretize exprs.

```{r Discretizing the data}
set.seed(3)
discretized_exprs <- FCBF::discretize_exprs_supervised(exprs, target)

```

Now that we have a discretized gene expression table, we can proceed to start making the network. 

```{r}
# get the SU scores
su_ic_vector <- FCBF::get_su(discretized_exprs, target)
su_ic_vector$gene <- rownames(su_ic_vector)

colnames(su_ic_vector)[1] <- 'SU'

fcbf_filtered <- FCBF::fcbf(discretized_exprs, target, thresh = 0.2, verbose = T)
fcbf_filtered$gene <- rownames(fcbf_filtered)

FCBF_genes <- gsub('\\.', '-', fcbf_filtered$gene)

```

There are two relevant table at the moment : the SU scored for all genes, and the genes selected by FCBF. 

Step 1:
    - Set an SU threshold to filter the total table
    
In this way, the genes that make up the final network will be related to the class of interest.


First, lets take a look at the distribution of SU values

```{r Distribution of SU Values}
FCBF::su_plot(discretized_exprs,target)
```

It seems as a threshold of 0.2 is ok. It was the one used for FCBF before anyway.  


```{r}

SU_threshold <- 0.2 

su_ic_vector_small <- su_ic_vector[su_ic_vector$SU > SU_threshold,]


SU_genes <- gsub('\\.', '-',su_ic_vector_small[,2])


exprs_small <- discretized_exprs[SU_genes ,]
```


Now we have what is needed to calculate the correlations for the network. 



```{r}
THIS IS BUGGY!!!
THE GET_SU HAS TO BE PROPERLY ORDERED!!!!!!
#'  su_i_j_matrix <- data.frame(genes =  SU_genes)
#'  
#'  
#'  # this can surely be improved for speed.
#'  for (i in SU_genes) {
#'          print(i)
#'          gene_i <- as.factor(discretized_exprs[i, ])
#'          gene_i_correlates <- FCBF::get_su(x = exprs_small, y = as.factor(exprs_small[i, ]))
#'          colnames(gene_i_correlates) <- i
#'          su_i_j_matrix[, i] <- gene_i_correlates[,1]
#'          
#'  }
```



Now we have an adjacency matrix composed by Symmetrical Uncertainty values. 

This already can be used for studying coexpression. Lin, Langfelder, Horvath explore these matrices in "Comparison of co-expression measures: Mutual information, correlation, and model based indices". A major limitation of the study is that they used only one (rather arbitrary) discretization method for calculating the mutual information. And they were working with bulk RNA-Seq simulations, the distribution of data points is rather different to single cell. Anyways.


Step 1:
    - Filter by SUij < SUic 
    
In this way, only associations that are stronger than the ones to the class are kept. 
This generates assymetry, as this can be true for SUic but not for SUjc.
We will handle this assymetry later. We will just, for now, call this our incidence matrix. 




```{r}

filtered_su_i_j_matrix <- data.frame(genes =  SU_genes)

for (i in colnames(su_i_j_matrix[,-1])){
  print(i)
  if (all(su_ic_vector$gene[seq_len(length(su_i_j_matrix$genes))] == su_i_j_matrix$genes)){
    
      tf_vector <- su_i_j_matrix[,i] < su_ic_vector$SU[seq_len(length(su_i_j_matrix$genes))] 
      
      filtered_su_i_j_matrix[,i] <- su_i_j_matrix[,i] * tf_vector
  }
}


```


This is our final matrix. We can apply classical module detection algorithms, such as DynamicTreeCut to test it.
Or we can consider the modules that FCBF provides.

For now, we will use FCBF modules in the following way:
  - Genes selected by FCBF will be considered seeds.
  - All genes j in a module must satisfy that SU(seed,j) > SU (j, class)
  
These are the genes that would be REMOVED by the FCBF algorithm.



```{r}

TODO --> EXPORT SU from FCBF!!
#' list_of_fcbf_modules <- list()
#' 
#' for (seed in fcbf_filtered$gene){
#'   
#'   su_i_j_matrix[,seed]
#'   
#'   print(seed)
#' }

```


  

